Bounded Model Checking for Embedded Systems \\ (Position Paper)

### 2016-01-04 paper.tex
fix references

\bibitem{leeCPS}
E.~Lee 
\newblock {\em Cyber-physical systems: Design challenges.} 
\newblock In: International Symposium on Object Oriented Real-Time Distributed Computing, pp. 363--369, 2008.

\bibitem{Kroening15}
Kroening D., Liang L., Melham T., Schrammel P., Tautschnig M.:
\newblock {\em Effective verification of low-level software with nested interrupts}. 
\newblock In: Design, Automation and Test in Europe, pp. 229--234, 2015.

@@

\bibitem{Lettnin09}
Lettnin D., Nalla P. K., Behrend J., Ruf J., Gerlach J., Kropf T., Rosenstiel W., Schönknecht V., Reitemeyer S.:
\newblock {\em Semiformal verification of temporal properties in automotive hardware dependent software}. 
\newblock In: Design, Automation and Test in Europe, pp. 1214--1217, 2009.

@@

\bibitem{Clarke04}
Clarke E., Kroening D., Lerda F.:
\newblock {\em A tool for checking {ANSI-C} programs.}
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems. LNCS 2988, Springer Berlin Heidelberg,  pp. 168--176, 2004.

\bibitem{MerzFS12}
Merz F., Falke S., Sinz C.:
\newblock {\em {LLBMC}: Bounded model checking of {C} and {C++} programs using a compiler {IR}.}
\newblock In: International Conference on Verified Software: Theories, Tools, Experiments. LNCS 7152, pp. 146--161, 2012.

\bibitem{CordeiroF11}
Cordeiro L., Fischer B.:
\newblock {\em Verifying multi-threaded software using {SMT}-based context-bounded model checking.}
\newblock In: International Conference on Software Engineering. ACM,  pp. 331--340, 2011.

\bibitem{Ivancic05}
Ivanicic F., Shlyakhter I., Gupta A., Ganai, M.K.:
\newblock {\em Model checking {C} programs using {F-Soft}.}
\newblock In: IEEE International Conference on Computer Design: VLSI in Computers and Processors, pp. 297--308, 2005.

\bibitem{Cordeiro12}
Cordeiro L., Fischer B., Marques{-}Silva J.:
\newblock {\em {SMT}-based bounded model checking for embedded {ANSI-C} software.}
\newblock {IEEE} Trans. Software Eng. \textbf{38}(4), pp. 957--974, 2012.

\bibitem{Donaldson10}
Donaldson A., Kroening D., R{\"{u}}mmer P.:
\newblock {\em {SCRATCH}: A tool for automatic analysis of {DMA} races.}
\newblock In: ACM Symposium on Principles and Practice of Parallel Programming. ACM, pp. 311--312, 2011.

@@

\bibitem{EenS03}
E{\'{e}}n, N., S{\"{o}}rensson, N.:
\newblock {\em Temporal induction by incremental {SAT} solving.}
\newblock Electronic Notes in Theoretical Computer Science \textbf{89}(4), pp. 543 -- 560, 2003.

\bibitem{GrosseLD09}
Gro{\ss}e D., Le H., Drechsler R.:
\newblock {\em Induction-based formal verification of {SystemC TLM} designs.}
\newblock In: International Workshop on Microprocessor Test and Verification, pp. 101--106, 2009.

\bibitem{Sheera00}
Sheeran M., Singh S., St{\aa}lmarck G.:
\newblock {\em Checking safety properties using induction and a {SAT}-solver.}
\newblock In: International Conference on Formal Methods in Computer-Aided Design. Springer-Verlag, pp. 108--125, 2000.

\bibitem{Gadelha15}
Gadelha M., Ismail H., Cordeiro L.:
\newblock {\em Handling loops in bounded model checking of C programs via \textit{k}-induction.}
\newblock In: International Journal on Software Tools for Technology Transfer (to appear), pp. 1--18, 2015.
\newblock http://dx.doi.org/10.1007/s10009-015-0407-9

@@

\bibitem{JMorse15}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {Model checking LTL properties over ANSI-C programs with bounded traces.}} 
\newblock In: Software and System Modeling 14(1): pp. 65--81, 2015.

>>>>

\bibitem{leeCPS}
E.~Lee 
\newblock {\em Cyber-physical Systems: Design Challenges.} 
\newblock In: International Symposium on Object Oriented Real-Time Distributed Computing, pp. 363--369, 2008.

\bibitem{Kroening15}
Kroening D., Liang L., Melham T., Schrammel P., Tautschnig M.:
\newblock {\em Effective Verification of Low-Level Software with Nested Interrupts}. 
\newblock In: Design, Automation and Test in Europe, pp. 229--234, 2015.

@@

\bibitem{Lettnin09}
Lettnin D., Nalla P. K., Behrend J., Ruf J., Gerlach J., Kropf T., Rosenstiel W., Schönknecht V., Reitemeyer S.:
\newblock {\em Semiformal Verification of Temporal Properties in Automotive Hardware Dependent Software}. 
\newblock In: Design, Automation and Test in Europe, pp. 1214--1217, 2009.

@@

\bibitem{Clarke04}
Clarke E., Kroening D., Lerda F.:
\newblock {\em A Tool for Checking {ANSI-C} Programs.}
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems. LNCS 2988, Springer Berlin Heidelberg,  pp. 168--176, 2004.

\bibitem{MerzFS12}
Merz F., Falke S., Sinz C.:
\newblock {\em {LLBMC}: Bounded Model Checking of {C} and {C++} Programs using a Compiler {IR}.}
\newblock In: International Conference on Verified Software: Theories, Tools, Experiments. LNCS 7152, pp. 146--161, 2012.

\bibitem{CordeiroF11}
Cordeiro L., Fischer B.:
\newblock {\em Verifying Multi-threaded Software using {SMT}-based Context-Bounded Model Checking.}
\newblock In: International Conference on Software Engineering. ACM,  pp. 331--340, 2011.

\bibitem{Ivancic05}
Ivanicic F., Shlyakhter I., Gupta A., Ganai, M.K.:
\newblock {\em Model Checking {C} Programs using {F-Soft}.}
\newblock In: IEEE International Conference on Computer Design: VLSI in Computers and Processors, pp. 297--308, 2005.

\bibitem{Cordeiro12}
Cordeiro L., Fischer B., Marques{-}Silva J.:
\newblock {\em {SMT}-based Bounded Model Checking for Embedded {ANSI-C} Software.}
\newblock {IEEE} Trans. Software Eng. \textbf{38}(4), pp. 957--974, 2012.

\bibitem{Donaldson10}
Donaldson A., Kroening D., R{\"{u}}mmer P.:
\newblock {\em {SCRATCH}: A Tool for Automatic Analysis of {DMA} Races.}
\newblock In: ACM Symposium on Principles and Practice of Parallel Programming. ACM, pp. 311--312, 2011.

@@

\bibitem{EenS03}
E{\'{e}}n, N., S{\"{o}}rensson, N.:
\newblock {\em Temporal Induction by Incremental {SAT} Solving.}
\newblock Electronic Notes in Theoretical Computer Science \textbf{89}(4), pp. 543 -- 560, 2003.

\bibitem{GrosseLD09}
Gro{\ss}e D., Le H., Drechsler R.:
\newblock {\em Induction-based Formal Verification of {SystemC TLM} Designs.}
\newblock In: International Workshop on Microprocessor Test and Verification, pp. 101--106, 2009.

\bibitem{Sheera00}
Sheeran M., Singh S., St{\aa}lmarck G.:
\newblock {\em Checking Safety Properties using Induction and a {SAT}-solver.}
\newblock In: International Conference on Formal Methods in Computer-Aided Design. Springer-Verlag, pp. 108--125, 2000.

\bibitem{Gadelha15}
Gadelha M., Ismail H., Cordeiro L.:
\newblock {\em Handling Loops in Bounded Model Checking of C Programs via \textit{k}-Induction.}
\newblock In: International Journal on Software Tools for Technology Transfer (to appear), pp. 1--18, 2015.
\newblock http://dx.doi.org/10.1007/s10009-015-0407-9

@@

\bibitem{JMorse15}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {Model Checking LTL Properties over ANSI-C Programs with Bounded Traces.}} 
\newblock In: Software and System Modeling 14(1): pp. 65--81, 2015.
